### 2025-05-16 chapters/haiti/haiti.Rnw
Addressing pre-defense comment: "Chapter titles must be in title case"
Fixing pre-defense review: "All figure and table captions must match word for word up to the first punctuation mark."

\chapter{Informing policy via dynamic models: Cholera in Haiti}
\label{chpt:haiti}

@@

# Plot reported cholera cases, by department. Creates Figure 1.
ggplot(dep_plot_df, aes(x = date, y = cases + 1)) +
  facet_wrap(~dep, nrow = 2, labeller = dep_labeller) +
  geom_line() +
  theme(axis.title.x = element_blank()) +
  ylab('Reported Cases') +
  scale_y_log10(
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  scale_x_date(
    date_labels = "'%y",
    breaks = seq.Date(
      from = as.Date("2011-01-01"),
      to = as.Date("2019-01-01"),
      by = '2 years'
    )
  )
@
\caption[Weekly cholera cases]{\label{fig:CholeraData}
Weekly reported cholera cases in Haiti from October 2010 to January 2019 for each of the 10 administrative departments.
}
\end{figure}

@@

References to the relevant equation are given in parentheses.

@@

\begin{table}
  \begin{center}
  \begin{tabular}{|c|c|c|c|c|}\hline
    \multirow{2}{*}{Parameter} & Our & \multicolumn{3}{c|}{Lee et al. (2020a)} \\\cline{3-5}
     & Notation & 1 & 2 & 3 \\
    \hline
    \hline
    Reporting Rate & $\reportRate$ & $\rho$ & $\rho$ & $\epsilon_1, \epsilon_2$ \\\hline
    Mixing Coefficient & $\mixExponent$ & $\nu$ & --- & --- \\\hline
    Measurement Over-Dispersion & $\obsOverdispersion$ & $\tau$ & --- & $p$ \\\hline
    Birth Rate & $\muBirth$ & $\mu$ & --- & --- \\\hline
    Natural Mortality Rate & $\muDeath$ & $\delta$ & --- & $\mu$ \\\hline
    Cholera Mortality Rate & $\choleraDeath$ & --- & --- & $\alpha$ \\\hline
    Latent Period & $1/\muEI$ & $1/\sigma$ & $1/\gamma_E$ & --- \\\hline
    Recovery Rate & $\muIR$ & $\gamma$ & $\gamma$ & $\gamma$ \\\hline
    Loss of Immunity & $\muRS$ & $\alpha$ & $\sigma$ & $\rho$ \\\hline
    Symptomatic Ratio & $\symptomFrac$ & $1 - \theta_0$ & $k$ & $\sigma$ \\\hline
    Asymptomatic Relative Infectiousness & $\asymptomRelativeInfect$ & $1-\kappa$ & $red_\beta$ & --- \\\hline
    Human-to-Water Shedding & $\Wshed$ & --- & $\mu$ & $\theta_I$ \\\hline
    Asymptomatic Relative Shedding & $\asymptomRelativeShed$ & --- & $red_\mu$ & $\theta_A/\theta_I$ \\\hline
    Seasonal Amplitude & $\seasAmplitude$ & --- & $\alpha_s$ & $\lambda$ \\\hline
    Transmission & $\transmission$ & $\beta$ & $\beta$ & $c$ \\\hline
    Water-to-Human & $\Wbeta{}$ & --- & $\beta_W$ & $\beta$ \\\hline
    Bacteria Mortality & $\Wremoval$ & --- & $\delta$ & $\mu_\beta$ \\\hline
    Vaccination Efficacy & $\vaccineEfficacy$ & $\theta_{vk}$ & $\theta_1, \theta_2, \theta_{1_5}, \theta_{2_5}$ & $\eta_{1d}, \eta_{2d}$ \\\hline
    Process Over-dispersion & $\sigmaProc$ & --- & --- & $\sigma_w$\\\hline
  \end{tabular}
  \end{center}
  \caption[Parameter translations to original model definitions]{\label{tab:translate}Translations between our common notation and notation used by Lee et al (2020).}
\end{table}

@@

\begin{table}[!h]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
 & \thead{Model~1} & \thead{Model~2} & \thead{Model~3}
\\
\hline
\hline
\multirow{2}{*}{Log-likelihood} &
  $\Sexpr{myround(mod1_ll, 1)}$ &
  $\Sexpr{myround(mod2_ll, 1)}$ &
  $\Sexpr{myround(mod3_ll, 1)}$ \\
    & ($\Sexpr{myround(mod1_lee_ll, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(unname(lee20_replication['leeFit_ll']), 1)}$) &
  ($\Sexpr{myround(lee3_results[["all_ll_eval"]], 1)}$)\footnotemark[2]
\\
\hline
Number of &
  $\Sexpr{as.character(mod1_n_params)}$ &
  $\Sexpr{as.character(mod2_n_params)}$ &
  $\Sexpr{as.character(mod3_n_params)}$ \\
 Fit Parameters &
 (\Sexpr{as.character(mod1_lee_n_params)}) &
 ($\Sexpr{as.character(unname(lee20_replication['leeFit_n_params']))}$) &
 ($\Sexpr{as.character(lee3_results$n_params, 1)}$)
\\
\hline
\multirow{2}{*}{AIC} &
  $\Sexpr{myround(mod1_aic, 1)}$ &
  $\Sexpr{myround(mod2_aic, 1)}$ &
  $\Sexpr{myround(mod3_aic, 1)}$ \\
  & ($\Sexpr{myround(mod1_lee_aic, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(mod2_lee_aic, 1)}$) &
  ($\Sexpr{myround(mod3_lee_coupled_aic, 1)}$)\footnotemark[2]
\\
\hline
\thead{Benchmark \\ AIC} &
  $\Sexpr{myround(-2 * benchmarks$m1 + 2 * 4, 1)}$ &
  $\Sexpr{myround(-2 * benchmarks$m2 + 2 * 40, 1)}$ &
  $\Sexpr{myround(-2 * benchmarks$m3 + 2 * 40, 1)}$
\\
\hline
\end{tabular}
\caption[AIC values for cholera models and benchmarks]{\label{tab:likes}AIC values for Models~1--3 and their benchmarks. Values in parentheses are corresponding values obtained using the models of \citet{lee20}. \textsuperscript{1}The reported likelihood is an upper bound of the likelihood of the model in \citet{lee20}. \textsuperscript{2}In \citet{lee20}, Model~3 was fit to a subset of the data (March 2014 onward, excluding data from Ouest in 2015-2016).
On this subset, their model has a likelihood of $\Sexpr{myround(lee3_results$sub_ll_eval, 1)}$.
On this same subset, our model has a likelihood of $\Sexpr{myround(mod3_eval_res$subset_ll['est'], 1)}$.
Details of estimating the likelihood of the models used in \citet{lee20} are provided in Appendix~\ref{sec:appendix_haiti_lee20}.}
\end{table}

@@

\begin{figure}[!h]
\centering
<<Beta_trend_Figure, fig.height=2.4, fig.width=3.6, fig.align='center'>>=
ggplot() +
  geom_point(data = h1_prof_res, aes(x = betat, y = logLik)) +
  geom_line(data = beta_t_mcap_results$fit, aes(x = parameter, y = smoothed), col = 'blue') +
  # geom_line(data = beta_t_mcap_results$fit, aes(x = parameter, y = quadratic), col = 'red') +
  geom_vline(xintercept = beta_t_mcap_results$ci[1], linetype = 'dashed') +
  geom_vline(xintercept = beta_t_mcap_results$ci[2], linetype = 'dashed') +
  geom_vline(xintercept = beta_t_mcap_results$mle, col = 'blue') +
  labs(x = "Log-Linear Trend in Transmission", y = 'Log Likelihood') +
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10))
@
\caption[Trend in transmission rate confidence interval.]{\label{fig:betat}
Monte Carlo adjusted profile (MCAP) of $\transmissionTrend$ for Model~1.
The blue curve is the MCAP, the vertical blue line indicates the MLE, and the vertical dashed lines indicate the $95\%$ confidence interval.
}
\end{figure}

@@

# Plot the data, median value of the simulation, and estimated quantiles.
ggplot() +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  geom_line(data = quants, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_ribbon(  # Plot confidence region
    data = quants,
    aes(x = date, ymin = q025 + 1, ymax = q975 + 1),
    alpha = 0.5
  ) +
  theme(
    axis.title.x = element_blank(),
    axis.text = element_text(size = 8),
    axis.title.y = element_text(size = 10)
  )+
  ylab('Reported cholera cases') +
  geom_vline(  # Show change from epidemic -> endemic models.
    xintercept = lubridate::weeks(232) + lubridate::ymd("2010-10-16"),
    linetype = 'dashed'
  ) +
  scale_y_log10(  # Plot on the log-scale
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  scale_x_date(  # Format the date on x-axis.
    date_labels = "'%y",
    breaks = seq.Date(
      from = as.Date("2011-01-01"),
      as.Date("2019-01-01"),
      by = '1 year'
    )
  )
@
\caption[Simulations from Model~1 compared to reported cholera cases.]{\label{fig:mod1fit}
The black curve is observed data, the blue curve is median of 500 simulations from initial conditions using estimated parameters, and the vertical dashed line represents break-point when parameters are refit.
}
\end{figure}

@@

\begin{figure}[!h]
<<Mod2Fit_and_Scenarios_Figure, fig.height=1.9, fig.width=4.8, fig.align='center'>>=
ggplot() +
  geom_line(data = h2_traj, aes(x = date, y = Ctotal + 1), col = 'blue') +
  geom_ribbon(
    data = h2_traj,
    aes(
      x = date,
      ymin = (Ctotal + 1) * exp(-1.96*h2_fit$h2_params['v']),
      ymax = (Ctotal + 1) * exp(1.96*h2_fit$h2_params['v'])
    ), alpha = 0.5
  ) +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  geom_line(
    data = filter(mod2_VaccScenarios$all_trajs, year >= max(h2_traj$year)),
    aes(x = as.Date(date), y = ReportedCases + 1, color = scenario)
  ) +
  geom_ribbon(
    data = filter(mod2_VaccScenarios$all_trajs, year >= max(h2_traj$year)) %>% filter(scenario == 'V0'),
    aes(
      x = as.Date(date),
      ymin = pmax((ReportedCases + 1) * exp(-1.96*h2_fit$h2_params['v']), 1),
      ymax = pmax((ReportedCases + 1) * exp(1.96*h2_fit$h2_params['v']), 1)
    ), linetype = 'dashed', alpha = 0.3
  ) +
  theme(axis.title.x = element_blank(),
        legend.title = element_blank(),
        axis.title.y = element_text(size = 9),
        axis.text = element_text(size = 8)) +
  ylab("Reported cholera cases") +
  scale_color_manual(values = c("V0" = '#f4a582',
                                "V1" = '#d6604d',
                                "V2" = '#b2182b',
                                "V3" = '#92c5de',
                                "V4" = '#4393c3')) +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  scale_x_date(date_labels = "'%y", breaks = seq.Date(from = as.Date("2010-01-01"), as.Date("2030-01-01"), by = '2 years'))
@
\caption[Simulated trajectory of Model~2]{\label{fig:mod2Traj}
The black line shows the nationally aggregated weekly cholera incidence data.
The blue curve from 2012-2019 is the trajectory of the calibrated version of Model~2.
Projections under the various vaccination scenarios, which are discussed in detail in the  {\bf Forecasts} subsection are also included. The gray ribbons represent a $95\%$ interval obtained from the log-normal measurement model. To avoid over-plotting, measurement variance is only plotted for the V0 vaccination scenario.}
\end{figure}

@@

# Plot the reported cases and confidence region for each department.
ggplot() +
  geom_line(data = h3_quants, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_line(data = dep_plot_df, aes(x = date, y = cases + 1), col = 'black') +
  geom_ribbon(  # plot confidence region.
    data = h3_quants,
    aes(x = date, ymin = q05 + 1, ymax = q95 + 1),
    alpha = 0.4
  ) +
  facet_wrap(
    ~factor(dep, levels = plot_order), nrow = 2, labeller = dep_labeller
  ) +
  labs(y = 'Log Reported Cholera Cases') +
  scale_x_date(  # Format the date on the X-axis.
    date_labels = "'%y",
    breaks = seq.Date(
      from = as.Date("2011-01-01"),
      to = as.Date("2019-01-01"),
      by = '2 years'
    )
  ) +
  theme(axis.title.x = element_blank()) +
  scale_y_log10(  # Plot on log-scale
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  )
@
\caption[Simulations from Model~3 compared to reported cholera cases.]{\label{fig:h3spatsims}
Simulations from initial conditions using the spatially coupled version of Model~3.
The black curve represents true case count, the blue line the median of 500 simulations from the model, and the gray ribbons representing $95\%$ confidence interval.
}
\end{figure}

@@

\begin{figure}[!h]
<<Model1_Seasonality_Figure, fig.height=2.9, fig.width=5, fig.align='center'>>=
cowplot::plot_grid(gg_rain, gg_trans, align = "v", ncol = 1)
@
\caption[Seasonality of Model 1 transmission rates and weekly rainfall.]{\label{fig:h1SeasRain}
(Top) weekly rainfall in Haiti, lighter colors representing more recent years.
(Bottom) estimated seasonality in the transmission rate (dashed line) plotted alongside mean rainfall (solid line).
The outsized effect of rainfall in the fall may be due to Hurricane Matthew, which struck Haiti in October of 2016 and resulted in an increase of cholera cases in the nation.
}
\end{figure}

@@

\begin{figure}[!h]
<<Elimination_Probs_Figure, fig.height=2.2>>=
ggplot(tidyr::drop_na(all_prob_elims), aes(x = time, y = elim_prob, col = mod)) +
  geom_line() +
  facet_wrap(~scenario, nrow = 1) +
  scale_color_manual(values = c("Model 1" = "#377eb8", "Model 3" = "#e41a1c")) +
  ylab("Probability of Elimination (%)") +
  theme(axis.title.x = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 35, hjust = 1),
        legend.margin=margin(c(-5, 0, -3, 0)),
        legend.box.margin = margin(c(-5, 0, -3, 0))) +
  scale_x_date(date_labels = "'%y", breaks = seq.Date(from = as.Date("2010-01-01"), as.Date("2030-01-01"), by = '2 years'))
@
\caption[Probability of cholera elimination under Models~1 and 3.]{\label{fig:elimProbs}
Probability of cholera elimination, defined as having zero cholera infectious for at least 52 consecutive weeks, based on 10 year simulations from calibrated versions of Models~1 and 3.
Compare to Figure~3A of \citet{lee20}.}
\end{figure}

>>>>

\chapter{Informing Policy via Dynamic Models: Cholera in Haiti}
\label{chpt:haiti}

@@

# Plot reported cholera cases, by department. Creates Figure 1.
ggplot(dep_plot_df, aes(x = date, y = cases + 1)) +
  facet_wrap(~dep, nrow = 2, labeller = dep_labeller) +
  geom_line() +
  theme(axis.title.x = element_blank()) +
  ylab('Reported Cases') +
  scale_y_log10(
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  scale_x_date(
    date_labels = "'%y",
    breaks = seq.Date(
      from = as.Date("2011-01-01"),
      to = as.Date("2019-01-01"),
      by = '2 years'
    )
  )
@
\caption[Weekly reported cholera cases in Haiti from October 2010 to January 2019.]{\label{fig:CholeraData}
Weekly reported cholera cases in Haiti from October 2010 to January 2019. Data are displayed for each of the 10 administrative departments.
}
\end{figure}

@@

Parameter estimates of the cholera models. References to the relevant equation are given in parentheses.

@@

\begin{table}
  \begin{center}
  \begin{tabular}{|c|c|c|c|c|}\hline
    \multirow{2}{*}{Parameter} & Our & \multicolumn{3}{c|}{Lee et al. (2020a)} \\\cline{3-5}
     & Notation & 1 & 2 & 3 \\
    \hline
    \hline
    Reporting Rate & $\reportRate$ & $\rho$ & $\rho$ & $\epsilon_1, \epsilon_2$ \\\hline
    Mixing Coefficient & $\mixExponent$ & $\nu$ & --- & --- \\\hline
    Measurement Over-Dispersion & $\obsOverdispersion$ & $\tau$ & --- & $p$ \\\hline
    Birth Rate & $\muBirth$ & $\mu$ & --- & --- \\\hline
    Natural Mortality Rate & $\muDeath$ & $\delta$ & --- & $\mu$ \\\hline
    Cholera Mortality Rate & $\choleraDeath$ & --- & --- & $\alpha$ \\\hline
    Latent Period & $1/\muEI$ & $1/\sigma$ & $1/\gamma_E$ & --- \\\hline
    Recovery Rate & $\muIR$ & $\gamma$ & $\gamma$ & $\gamma$ \\\hline
    Loss of Immunity & $\muRS$ & $\alpha$ & $\sigma$ & $\rho$ \\\hline
    Symptomatic Ratio & $\symptomFrac$ & $1 - \theta_0$ & $k$ & $\sigma$ \\\hline
    Asymptomatic Relative Infectiousness & $\asymptomRelativeInfect$ & $1-\kappa$ & $red_\beta$ & --- \\\hline
    Human-to-Water Shedding & $\Wshed$ & --- & $\mu$ & $\theta_I$ \\\hline
    Asymptomatic Relative Shedding & $\asymptomRelativeShed$ & --- & $red_\mu$ & $\theta_A/\theta_I$ \\\hline
    Seasonal Amplitude & $\seasAmplitude$ & --- & $\alpha_s$ & $\lambda$ \\\hline
    Transmission & $\transmission$ & $\beta$ & $\beta$ & $c$ \\\hline
    Water-to-Human & $\Wbeta{}$ & --- & $\beta_W$ & $\beta$ \\\hline
    Bacteria Mortality & $\Wremoval$ & --- & $\delta$ & $\mu_\beta$ \\\hline
    Vaccination Efficacy & $\vaccineEfficacy$ & $\theta_{vk}$ & $\theta_1, \theta_2, \theta_{1_5}, \theta_{2_5}$ & $\eta_{1d}, \eta_{2d}$ \\\hline
    Process Over-dispersion & $\sigmaProc$ & --- & --- & $\sigma_w$\\\hline
  \end{tabular}
  \end{center}
  \caption{\label{tab:translate}Parameter translations between our common notation and notation used by Lee et al (2020).}
\end{table}

@@

\begin{table}[!h]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
 & \thead{Model~1} & \thead{Model~2} & \thead{Model~3}
\\
\hline
\hline
\multirow{2}{*}{Log-likelihood} &
  $\Sexpr{myround(mod1_ll, 1)}$ &
  $\Sexpr{myround(mod2_ll, 1)}$ &
  $\Sexpr{myround(mod3_ll, 1)}$ \\
    & ($\Sexpr{myround(mod1_lee_ll, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(unname(lee20_replication['leeFit_ll']), 1)}$) &
  ($\Sexpr{myround(lee3_results[["all_ll_eval"]], 1)}$)\footnotemark[2]
\\
\hline
Number of &
  $\Sexpr{as.character(mod1_n_params)}$ &
  $\Sexpr{as.character(mod2_n_params)}$ &
  $\Sexpr{as.character(mod3_n_params)}$ \\
 Fit Parameters &
 (\Sexpr{as.character(mod1_lee_n_params)}) &
 ($\Sexpr{as.character(unname(lee20_replication['leeFit_n_params']))}$) &
 ($\Sexpr{as.character(lee3_results$n_params, 1)}$)
\\
\hline
\multirow{2}{*}{AIC} &
  $\Sexpr{myround(mod1_aic, 1)}$ &
  $\Sexpr{myround(mod2_aic, 1)}$ &
  $\Sexpr{myround(mod3_aic, 1)}$ \\
  & ($\Sexpr{myround(mod1_lee_aic, 1)}$)\footnotemark[1] &
  ($\Sexpr{myround(mod2_lee_aic, 1)}$) &
  ($\Sexpr{myround(mod3_lee_coupled_aic, 1)}$)\footnotemark[2]
\\
\hline
\thead{Benchmark \\ AIC} &
  $\Sexpr{myround(-2 * benchmarks$m1 + 2 * 4, 1)}$ &
  $\Sexpr{myround(-2 * benchmarks$m2 + 2 * 40, 1)}$ &
  $\Sexpr{myround(-2 * benchmarks$m3 + 2 * 40, 1)}$
\\
\hline
\end{tabular}
\caption[AIC values for cholera models and benchmarks.]{\label{tab:likes}AIC values for cholera models and benchmarks. Values in parentheses are corresponding values obtained using the models of \citet{lee20}. \textsuperscript{1}The reported likelihood is an upper bound of the likelihood of the model in \citet{lee20}. \textsuperscript{2}In \citet{lee20}, Model~3 was fit to a subset of the data (March 2014 onward, excluding data from Ouest in 2015-2016).
On this subset, their model has a likelihood of $\Sexpr{myround(lee3_results$sub_ll_eval, 1)}$.
On this same subset, our model has a likelihood of $\Sexpr{myround(mod3_eval_res$subset_ll['est'], 1)}$.
Details of estimating the likelihood of the models used in \citet{lee20} are provided in Appendix~\ref{sec:appendix_haiti_lee20}.}
\end{table}

@@

\begin{figure}[!h]
\centering
<<Beta_trend_Figure, fig.height=2.4, fig.width=3.6, fig.align='center'>>=
ggplot() +
  geom_point(data = h1_prof_res, aes(x = betat, y = logLik)) +
  geom_line(data = beta_t_mcap_results$fit, aes(x = parameter, y = smoothed), col = 'blue') +
  # geom_line(data = beta_t_mcap_results$fit, aes(x = parameter, y = quadratic), col = 'red') +
  geom_vline(xintercept = beta_t_mcap_results$ci[1], linetype = 'dashed') +
  geom_vline(xintercept = beta_t_mcap_results$ci[2], linetype = 'dashed') +
  geom_vline(xintercept = beta_t_mcap_results$mle, col = 'blue') +
  labs(x = "Log-Linear Trend in Transmission", y = 'Log Likelihood') +
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 10))
@
\caption[Confidence interval for linear trend in transmission rate.]{\label{fig:betat}
Confidence interval for linear trend in transmission rate. The confidence interval is calculated using Monte Carlo adjusted profile (MCAP) of $\transmissionTrend$ for Model~1.
The blue curve is the MCAP, the vertical blue line indicates the MLE, and the vertical dashed lines indicate the $95\%$ confidence interval.
}
\end{figure}

@@

# Plot the data, median value of the simulation, and estimated quantiles.
ggplot() +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  geom_line(data = quants, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_ribbon(  # Plot confidence region
    data = quants,
    aes(x = date, ymin = q025 + 1, ymax = q975 + 1),
    alpha = 0.5
  ) +
  theme(
    axis.title.x = element_blank(),
    axis.text = element_text(size = 8),
    axis.title.y = element_text(size = 10)
  )+
  ylab('Reported cholera cases') +
  geom_vline(  # Show change from epidemic -> endemic models.
    xintercept = lubridate::weeks(232) + lubridate::ymd("2010-10-16"),
    linetype = 'dashed'
  ) +
  scale_y_log10(  # Plot on the log-scale
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  ) +
  scale_x_date(  # Format the date on x-axis.
    date_labels = "'%y",
    breaks = seq.Date(
      from = as.Date("2011-01-01"),
      as.Date("2019-01-01"),
      by = '1 year'
    )
  )
@
\caption[Simulations from Model~1 compared to reported cholera cases.]{\label{fig:mod1fit}
Simulations from Model~1 compared to reported cholera cases. The black curve is observed data, the blue curve is median of 500 simulations from initial conditions using estimated parameters, and the vertical dashed line represents break-point when parameters are refit.
}
\end{figure}

@@

\begin{figure}[!h]
<<Mod2Fit_and_Scenarios_Figure, fig.height=1.9, fig.width=4.8, fig.align='center'>>=
ggplot() +
  geom_line(data = h2_traj, aes(x = date, y = Ctotal + 1), col = 'blue') +
  geom_ribbon(
    data = h2_traj,
    aes(
      x = date,
      ymin = (Ctotal + 1) * exp(-1.96*h2_fit$h2_params['v']),
      ymax = (Ctotal + 1) * exp(1.96*h2_fit$h2_params['v'])
    ), alpha = 0.5
  ) +
  geom_line(data = true_agg_cases, aes(x = date, y = ReportedAll + 1)) +
  geom_line(
    data = filter(mod2_VaccScenarios$all_trajs, year >= max(h2_traj$year)),
    aes(x = as.Date(date), y = ReportedCases + 1, color = scenario)
  ) +
  geom_ribbon(
    data = filter(mod2_VaccScenarios$all_trajs, year >= max(h2_traj$year)) %>% filter(scenario == 'V0'),
    aes(
      x = as.Date(date),
      ymin = pmax((ReportedCases + 1) * exp(-1.96*h2_fit$h2_params['v']), 1),
      ymax = pmax((ReportedCases + 1) * exp(1.96*h2_fit$h2_params['v']), 1)
    ), linetype = 'dashed', alpha = 0.3
  ) +
  theme(axis.title.x = element_blank(),
        legend.title = element_blank(),
        axis.title.y = element_text(size = 9),
        axis.text = element_text(size = 8)) +
  ylab("Reported cholera cases") +
  scale_color_manual(values = c("V0" = '#f4a582',
                                "V1" = '#d6604d',
                                "V2" = '#b2182b',
                                "V3" = '#92c5de',
                                "V4" = '#4393c3')) +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  scale_x_date(date_labels = "'%y", breaks = seq.Date(from = as.Date("2010-01-01"), as.Date("2030-01-01"), by = '2 years'))
@
\caption[Simulated trajectory of cholera incidence using Model~2.]{\label{fig:mod2Traj}
Simulated trajectory of cholera incidence using Model~2.
The black line shows the nationally aggregated weekly cholera incidence data.
The blue curve from 2012-2019 is the trajectory of the calibrated model.
Projections under the various vaccination scenarios, which are discussed in detail in the  {\bf Forecasts} subsection are also included. The gray ribbons represent a $95\%$ interval obtained from the log-normal measurement model. To avoid over-plotting, measurement variance is only plotted for the V0 vaccination scenario.}
\end{figure}

@@

# Plot the reported cases and confidence region for each department.
ggplot() +
  geom_line(data = h3_quants, aes(x = date, y = q50 + 1), col = 'blue') +
  geom_line(data = dep_plot_df, aes(x = date, y = cases + 1), col = 'black') +
  geom_ribbon(  # plot confidence region.
    data = h3_quants,
    aes(x = date, ymin = q05 + 1, ymax = q95 + 1),
    alpha = 0.4
  ) +
  facet_wrap(
    ~factor(dep, levels = plot_order), nrow = 2, labeller = dep_labeller
  ) +
  labs(y = 'Log Reported Cholera Cases') +
  scale_x_date(  # Format the date on the X-axis.
    date_labels = "'%y",
    breaks = seq.Date(
      from = as.Date("2011-01-01"),
      to = as.Date("2019-01-01"),
      by = '2 years'
    )
  ) +
  theme(axis.title.x = element_blank()) +
  scale_y_log10(  # Plot on log-scale
    labels = scales::trans_format("log10", scales::math_format(10^.x))
  )
@
\caption[Simulations from Model~3 compared to reported cholera cases.]{\label{fig:h3spatsims}
Simulations from Model~3 compared to reported cholera cases. Simulations were obtained using the initial conditions of Model~3 calibrated to data.
The black curve represents true case count, the blue line the median of 500 simulations from the model, and the gray ribbons representing $95\%$ confidence interval.
}
\end{figure}

@@

\begin{figure}[!h]
<<Model1_Seasonality_Figure, fig.height=2.9, fig.width=5, fig.align='center'>>=
cowplot::plot_grid(gg_rain, gg_trans, align = "v", ncol = 1)
@
\caption[Seasonality of Model 1 transmission rates and weekly rainfall.]{\label{fig:h1SeasRain}
Seasonality of Model 1 transmission rates and weekly rainfall.
(Top) weekly rainfall in Haiti, lighter colors representing more recent years.
(Bottom) estimated seasonality in the transmission rate (dashed line) plotted alongside mean rainfall (solid line).
The outsized effect of rainfall in the fall may be due to Hurricane Matthew, which struck Haiti in October of 2016 and resulted in an increase of cholera cases in the nation.
}
\end{figure}

@@

\begin{figure}[!h]
<<Elimination_Probs_Figure, fig.height=2.2>>=
ggplot(tidyr::drop_na(all_prob_elims), aes(x = time, y = elim_prob, col = mod)) +
  geom_line() +
  facet_wrap(~scenario, nrow = 1) +
  scale_color_manual(values = c("Model 1" = "#377eb8", "Model 3" = "#e41a1c")) +
  ylab("Probability of Elimination (%)") +
  theme(axis.title.x = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 35, hjust = 1),
        legend.margin=margin(c(-5, 0, -3, 0)),
        legend.box.margin = margin(c(-5, 0, -3, 0))) +
  scale_x_date(date_labels = "'%y", breaks = seq.Date(from = as.Date("2010-01-01"), as.Date("2030-01-01"), by = '2 years'))
@
\caption[Probability of cholera elimination under Models~1 and 3.]{\label{fig:elimProbs}
Probability of cholera elimination under Models~1 and 3. Elimination is defined as having zero cholera infectious for at least 52 consecutive weeks, based on 10 year simulations from the calibrated models.
Compare to Figure~3A of \citet{lee20}.}
\end{figure}
